Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2014-04-07 parts/example.tex
change footnote + personal address
reachability on the metazoan example

@@

The Boolean model has been automatically encoded into a Process Hitting with 2 classes of priority%
\footnote{Model and scripts are available at
\url{http://www.irccyn.ec-nantes.fr/~folschet/underapprox-tcrsig94.zip}.}.
Then, we verified the reachability for the independent activation of 4 outputs of the signalling
cascade (SRE, AP1, NFkB, NFAT) from all possible input combinations (CD45, CD28, TCRlib) using our
new reachability under-approximation (answering either \emph{yes} or \emph{inconclusive}) and a 
previously defined reachability over-approximation \cite{PMR12-MSCS} (answering either \emph{no} or
\emph{inconclusive}).
All result in conclusive decisions, and the under-approximation has been satisfied in 12 cases (over
32) proving the satisfiability of the concerned reachability property in the encoded Boolean network
(and non-satisfiability in the other cases).

>>>>

The static analysis results of \pref{ssec:ua} and \pref{ssec:ordered-ua} can be used to check if the model is functional, \ie
if genes $a$ and $c$ are successively activated and deactivated,
thus leading to the formation of regular stripes.
Starting from context $\ctx = \PHstate{f_1, a_0, c_0}$,
we want to check the reachability of
$\w = \PHobj{a_0}{a_1} \PHconcat \PHobj{c_0}{c_1} \PHconcat \PHobj{a_1}{a_0} \PHconcat \PHobj{c_1}{c_0}$.
Rather than checking this whole objective sequence,
we decompose it into the following ones:
\begin{align*}
  \ctx^1 &= \PHstate{f_1, a_0, c_0} \text{ and } P_1 = \PHobj{a_0}{a_1} &
  \ctx^3 &= \PHstate{f_1, a_1, c_1} \text{ and } P_2 = \PHobj{a_1}{a_0} \\
  \ctx^2 &= \PHstate{f_1, a_1, c_0} \text{ and } P_3 = \PHobj{c_0}{c_1} &
  \ctx^4 &= \PHstate{f_1, a_0, c_1} \text{ and } P_4 = \PHobj{c_1}{c_0}
\end{align*}
Given \pref{th:approxinf}, we have: $\forall i \in \segm{1}{4}, \muconcr_{\ctx^i}(P_i) \neq \emptyset$.
Finally, after checking that it can be applied for $i = 3$ down to $i = 1$,
\pref{thm:ordered-ua} gives: $\uconcr(\w) \neq \emptyset$.
Thus the model is functional.

@@

The Boolean model has been automatically encoded into a Process Hitting with 2 classes of priority%
\footnote{Files are available at
\url{http://maxime.folschette.name/underapprox-tcrsig94.zip}.}.
Then, we verified the reachability for the independent activation of 4 outputs of the signalling
cascade (SRE, AP1, NFkB, NFAT) from all possible input combinations (CD45, CD28, TCRlib) using our
new reachability under-approximation (answering either \emph{yes} or \emph{inconclusive}) and a 
previously defined reachability over-approximation \cite{PMR12-MSCS} (answering either \emph{no} or
\emph{inconclusive}).
All result in conclusive decisions, and the under-approximation has been satisfied in 12 cases (over
32) proving the satisfiability of the concerned reachability property in the encoded Boolean network
(and non-satisfiability in the other cases).
